---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# range

<!-- badges: start -->
<!-- badges: end -->

The goal of _range_, which contains the "range" function, is to provide a more convenient way to calculate the difference between the largest and smallest number in a numerical vector.

## Installation

You can install the released version of range from [CRAN](https://CRAN.R-project.org) with:

```{r}
devtools::install_github("ayshaab/range")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(range)
range(1:10)
```

## How each part of this R package was made

To initially create a new file path for the _range_ package (.Rproj.user folder, R folder, NAMESPACE file and DESCRIPTION file):

```{r}
library(devtools) #I first loaded the devtools package
create_package("~/Desktop/range")
```

Then I initialized the range package to a git repository:

```{r}
library(devtools) #I first loaded the devtools package
use_git()
```

I wrote my r function which will appear as a range.R file within the R folder of this package:

```{r}
library(devtools) #I first loaded the devtools package
use_r("range")

#Within this newly created file, I wrote my function and loaded this function using:
load_all() 
#Checked that all the files created so far is correct using:
check()
```

To edit the description file I manually changed the following lines:
1) Title
2) Person (i.e. first and last name, and email)
3) Description
4) License
```{r}
#To change the license
use_mit_license("Aysha Allard Brown")
#The new output should now be MIT + file LICENSE and a new LICENSE.md file should have been created
```

To make an R documentation file for the range function:

```{r}
library(roxygen2)
#Then code> insert Roxygen skeleton 
#To render this documentation
document()
```

For my package to include tests:

```{r}
library(devtools) #I first loaded the devtools package
use_testthat()
#To initialize a basic test file and open it for editing
use_test("range")
```

To depend on the purrr package (to add purrr to the Imports field in the DESCRIPTION file:

```{r}
use_package("purrr")
document() #Run this and run test() to make sure everything's working fine
```


To build this README.Rmd file:

```{r}
library(devtools) #I first loaded the devtools package
use_readme_rmd()
#Then I built my READMe.Rmd file
build_readme()
```

To make a vignette:
```{r}
use_vignette("range")
#Then I built my vignette
build_vignettes()
```
